### 2015-03-05 paper_70_case-study.tex
added overall scores for case study

        \subsubsection{OVERALL}
            All of the months do not include the same elements.

    An CRI calculation analyzing historical performance.

>>>>

        \subsubsection{OVERALL}
            Now it is time to combine the scores for the overall CRI.  Notice
            the schedule does not have scores for January 2014 or January 2015.
            Presumably, that is because the SDO within the large financial institution
            does not schedule projects to be completed in January. Much of the work
            would need to be completed over Christmas and New Year's Day, but many
            workers take personal time off of work during that time.  Thus some
            organizations will schedule appropriately.  CRI is well suited to
            handle this problem.  Just perform a weighted average over the
            applicable elements.  In this case study, the weights are all equal,
            so CRI is just a straight average.  Figure \ref{fig:cri-scores}
            displays the CRI scores as computed with the source code
            from Appendix \ref{src:overall}.  The scores are all above 0, so this
            financial institution is consistently performing better
            than expected.

            \begin{figure}[ht]
                \centering
                \includegraphics[scale=.3]{images/cri_scores.png}
                \caption{CRI SCORES}
                \label{fig:cri-scores}
            \end{figure}
